README

### 2017-04-11 src/README.Rmd
Add articles for review in CSV along with notes about them
Still need to left join these data

```{r library, message=FALSE}
library(dplyr)

@@

>>>>

```{r library, message=FALSE}
library(dplyr)
library(readr)

@@

# Joining articles with assignees
The articles were searched for and citations were downloaded, DOIs were saved in a CSV file with notes related to the articles and selections. Using this CSV file along with a CSV file generated from an export of the bibliography information from Zotero, join the two files.

```{r join_files}
articles <- read.csv("data/Journals_for_review.csv", strip.white = TRUE)

notes <- read.csv("data/Article_notes.csv", strip.white = TRUE)

# todo join articles and notes
